Unshuffling Permutations

### 2015-06-29 article.tex
Partie algebre (suite)

\usepackage[utf8x]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
%\usepackage{llncsdoc}
\usepackage[english]{babel}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{todonotes}
\usepackage{subfigure}

@@

\begin{proposition}
    Let $\pi$ be a square permutation and $\rho$ a square root of $\pi$.
    Then,
    \begin{enumerate}
        \item the permutation $\pi^\sim$ is a square and $\rho^\sim$
        is one of its square roots;
        \item the permutation $\bar \pi$ is a square and $\bar \rho$
        is one of its square roots;
        \item the permutation $\pi^{-1}$ is a square and $\rho^{-1}$
        is one of its square roots.
    \end{enumerate}
\end{proposition}
\begin{proof}

>>>>

\usepackage[utf8x]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
%\usepackage{llncsdoc}
\usepackage[english]{babel}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{todonotes}
\usepackage{subfigure}
\usepackage{enumitem}

@@

\begin{proposition} \label{prop:square_stability}
    Let $\pi$ be a square permutation and $\rho$ a square root of $\pi$.
    Then,
    \begin{enumerate}[label={\it (\roman*)},fullwidth]
        \item \label{item:square_stability_1}
        the permutation $\pi^\sim$ is a square and $\rho^\sim$
        is one of its square roots;
        \item \label{item:square_stability_2}
        the permutation $\bar \pi$ is a square and $\bar \rho$
        is one of its square roots;
        \item \label{item:square_stability_3}
        the permutation $\pi^{-1}$ is a square and $\rho^{-1}$
        is one of its square roots.
    \end{enumerate}
\end{proposition}
\begin{proof}
    First of all, since $\pi$ is a square permutation and $\rho$ is a
    square root of $\pi$, $\pi$ appears in $\rho \bullet \rho$. In
    an equivalent way, this amounts to say that $\rho \otimes \rho$ has
    a nonzero coefficient in the expansion of $\Delta(\pi)$. This
    implies that there are two disjoint sets of indexes $P_1$ and $P_2$
    such that $P_1 \uplus P_2 = [|\pi|]$ and
    \begin{equation} \label{equ:square_stability_same_std}
        \STD\left(\pi_{|P_1}\right) = \rho = \STD\left(\pi_{|P_2}\right).
    \end{equation}
    \smallskip

    To prove~\ref{item:square_stability_1}, set
    $P_1^\sim := \{|\pi| - i  + 1 : i \in P_1\}$ and
    $P_2^\sim := \{|\pi| - i  + 1 : i \in P_2\}$.
    Since~\eqref{equ:square_stability_same_std} holds, one has
    \begin{equation}
        \STD\left(\pi^\sim_{|P_1^\sim}\right) = \rho^\sim =
        \STD\left(\pi^\sim_{|P_2^\sim}\right).
    \end{equation}

    TO CONTINUE
